---
title:  params$vrc"Neutralization Report"
author: "Ashley Clark"
date: "`r format(Sys.time(), '%b %d, %Y')`"
output: html_document
params:
  production: TRUE
  cutpoint: 1
  vrc: "VRC01"
  pgt: "PGT122"
---

```{r, set-chunk-opts, echo = FALSE, eval = params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, load-data}
data_url <- "https://bit.ly/vrc01_data"
vrc <- read.csv(data_url, header = TRUE)
```

```{r,load-data2}
data_url2 <- "https://bit.ly/pgt122_data"
pgt <- read.csv(data_url, header = TRUE)
```

# Descriptive Analysis

## Tabular analysis

Characteristics of the `r nrow(data)` viruses from the CATNAP database are displayed
in the table below.

```{r, table1, echo=FALSE}
library(labelled)
library(gtsummary)

var_label(vrc) <- list ( 
  id = "ID",
  ab_resistance = "Antibiotic resistance",
  shield_glycans = "shield",
  region = "Region",
  env_length = " Length of Env protein"
  )
vrc$number_glycans <- ifelse(vrc$shield_glycans < 4, "< 4",">= 4")

vrc %>% 
  select("region", "env_length", "ab_resistance", "number_glycans") %>%  
  tbl_summary(by = number_glycans) %>% 
modify_spanning_header(c("stat_1","stat_2") ~ "**PNGs in Glycan Shield**") %>% 
  add_overall() %>%  
  add_p()
```

## Graphical analysis

Below we report a scatter plot of antibody resistance as a function of 
number of PNGs in the glycan shield. 

```{r, plot-data}
#| fig.align = "center",
#| out.width = "100px"
library(ggplot2)

ggplot(vrc, aes(x = shield_glycans, y = ab_resistance)) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_bw()

```

# Regression Analysis

## Primary model

```{r, fit-primary-model}
mod <- glm(
  ab_resistance ~ shield_glycans + region + env_length,
  data = data
)

tbl_regression(mod) |>
  add_global_p()
```

## Secondary model

In this analysis, we generated a binary outcome where level 1 of the outcome
means the antibody resistance score was greater than `r params$cutpoint`.

```{r, secondary-model}
binary_mod <- glm(
  I(ab_resistance > params$cutpoint) ~ shield_glycans + region + env_length,
  data = vrc,
  family = binomial()
)

tbl_regression(binary_mod, exponentiate = TRUE) |>
  add_global_p()
```



















