---
title: "R Markdown Part 2 Notes"
author: "Ashley Clark"
date: "2025-09-17"
output: pdf_document
params: 
  production: TRUE
  cutpoint: 1
---

```{r,production-or-test, echo=FALSE}
# we will learn a better approach to this 
production <- TRUE 
```

```{r,set-chunk-opts, eval= params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

# RMarkdown Part 2
## \textcolor{pink}{4.1 Installing Required Packages} 

```{r, Packages,}
library(labelled)
library(gtsummary)
```

## \textcolor{pink}{4.2 Options for creating tables in R markdown}

* Print a data.frame or matrix 
  	* Easy, but monospaced format
  	
* Knitr::kable
    * Easy, nice looking – not 100% flexible 
* Gt
    * Tidyverse compatible syntax, highly flexible, but only html for now 
* Xtable:xtable 
    * Highly customizable, but only for pdfs (LaTex based) 
* Pander::pander
    * Default tables for different R classes
* Stargazer::stargazer

## \textcolor{pink}{4.3 Creating Table 1 using gtsummary}

First, create new rmarkdown document 
```{r, load-data, echo=FALSE}
Data_url <- "https://bit.ly/vrc01_data"
Gly <- read.csv(Data_url, header = TRUE)
```
## Descriptive Analysis 
### Tabular analysis 
Characteristics of the `r nrow(data)` virus from the CATNAP database are displayed in the table below. 

```{r, table1, echo=FALSE}
library(labelled)
library(gtsummary)
var_label(Gly) <- list ( 
  id = "ID",
  ab_resistance = "Antibiotic resistance",
  shield_glycans = "shield",
  region = "Region",
  env_length = " Length of Env protein"
  )
Gly$number_glycans <- ifelse(Gly$shield_glycans < 4, "< 4",">= 4")

Gly %>% 
  select("region", "env_length", "ab_resistance", "number_glycans") %>%  
  tbl_summary(by = number_glycans) %>% 
modify_spanning_header(c("stat_1","stat_2") ~ "**PNGs in Glycan Shield**") %>% 
  add_overall() %>%  
  add_p()
```
## \textcolor{pink}{4.5 Fitting and Summarizing Regression Model in R Markdown}

# Regression Analysis 
## Primary Model
```{r, fit-primary model}
mod <- glm(
  ab_resistance ~ shield_glycans + region + env_length,
  data = Gly
)
tbl_regression(mod) %>% 
  add_global_p()

```
## Secondary model 

In this analysis, we generated a binary outcome where level 1 of the outcome means the antibody resistance score was greater than `r params$cutpoint`. 

```{r, secondary-model}
binary_mod <- glm (
  I(ab_resistance > params$cutpoint) ~ shield_glycans + region + env_length, 
  data = Gly,
  family = binomial ()
)

tbl_regression(binary_mod, exponentiate = TRUE) %>% 
  add_global_p()
```

## \textcolor{pink}{4.6 Adding figures to an R Markdown document }

## Graphical Analysis 

Below we report a scatter plot of antibody resistance as a function of number of PNGs in the glycan shield. 
```{r, plot-data, echo=FALSE, message=FALSE, fig.align='center', out.width="400px"}
library(ggplot2)

ggplot(Gly, aes(x=shield_glycans, y= ab_resistance)) +
  geom_point() +
  geom_smooth(method=lm) + 
  theme_classic()
```
## \textcolor{pink}{ 4.7 Setting Global Chunk Options}

* Useful if you don't want code chunks to show in rendered rmarkdown document 
* "Set Chunk Opts at Top"

## \textcolor{pink}{4.8 Dynamically setitng code chunk options}

* production or test chunk at the top 
  * creates flag if this report was for two different audiences 

## \textcolor{pink}{4.10 Parameterized R Markdown reports}

1. new rmarkdown file? 

option added to yaml header 

"params:" "variable1: 10, variable2: 20, variable3: 30"

```{r,check-variable1}
print("The value of variable 1 is...")
print (params$variable1)
```














